\section{Conclusion}

In this paper, we propose \textbf{\model{}}, a framework that enables users to effectively interact with human “dreams” and influence final presentations.
Our framework offers several appealing properties:
1) We \emph{pioneer a novel interaction paradigm with the human brain} by introducing a prototype that directly instructs fMRI signals via natural language descriptions, opening up exciting possibilities for future applications.
2) Our model's capability can be further enhanced using techniques that consider temporal and spatial perspectives, thereby improving the fidelity and precision of instructions.
3) With minimal effort, our system can seamlessly extend to support multi-modal instructions.

\paragraph{Limitations and Future Work.} 1) In this work, we consider the obtained biological brain signals from visual stimuli as representations of human ``thoughts''. However, in real-world applications, the situation is more complex. ``Dreams,'' for instance, might originate from internal brain activity rather than external stimuli. 2) Our model struggles with instructions involving the addition of small objects. 3) For the LLM-enhanced region-aware instructions, an extra forward process is required to first extract the instruction-relevant regions from the intermediate reconstructions. 4) Future work will explore other types of ``dreams,'' such as audio and text, and more complex interaction strategies, such as multi-turn conversations.

% sophisticated strategies, such as Chain-of-Thought (CoT), to efficiently and effectively employ LLM agents for high-fidelity instructions.

\paragraph{Ethical Issues.} As the title suggests, this model can be potentially exploited for malicious purposes such as mis-interpreting thoughts within human brain. We are committed to limiting the usage of our model strictly to research purposes. 


% \textbf{Author Contributions.}

% Mingchen initialized the idea and helped draft the current version of the abstract and introduction.